Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-27 manuscript/manuscript.tex
add Juhye reference to paper

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figures/empirical_trees.pdf}}
\caption{\label{fig:empirical_trees}
\textbf{Effect of site-specific stationary state and $\Gamma\omega$ rate variation on HA branch length estimation.} 
The branch lengths of the HA tree are optimized using the indicated ExpCM and GY94 models. 
The amino-acid preferences defining the model (ExpCM) or implied by the model (GY94) are shown as logoplots for \jdbcomment{? example sites in HA; the full set of experimentally measured amino-acid preferences defining each ExpCM are shown in ?}. 
The ExpCM's use amino-acid preferences measured in deep mutational scanning of an H1 HA~\cite{doud2016accurate}, an H3 HA~\jdbcomment{Lee citation}, or the average of the measurements for these two HAs.
The circle denotes the H1 clade and the triangle denotes the H3 clade. 
}
\end{figure}

@@

There are two deep mutational scanning datasets for HA that estimated amino-acid preferences for all sites.
One scan measured the site-specific amino-acid preferences of an H1 HA~\citep{doud2016accurate} and the other measured the preferences of an H3 HA\jdbcomment{Lee citation}.
These two HAs have only $\sim$42\% amino-acid identity, and so are separated by a large distance on the phylogenetic tree (see triangle and circle on \ref{fig:empirical_trees}).
The experimentally measured amino-acid preferences clearly differ between the the H1 and H3 HA at a substantial number of sites\jdbcomment{Lee citation, maybe also refer to your own supplementary figures}.
Therefore, we also created a third set of amino-acid preferences by averaging the preferences measured in the deep mutational scanning of the H1 and H3 HAs, under the conjecture that these averaged preferences might do a better job of describing the ``average'' constraint on sites across the full HA tree.
These three sets of HA amino-acid preferences define three different ExpCM's.

>>>>

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figures/empirical_trees.pdf}}
\caption{\label{fig:empirical_trees}
\textbf{Effect of site-specific stationary state and $\Gamma\omega$ rate variation on HA branch length estimation.} 
The branch lengths of the HA tree are optimized using the indicated ExpCM and GY94 models. 
The amino-acid preferences defining the model (ExpCM) or implied by the model (GY94) are shown as logoplots for \jdbcomment{? example sites in HA; the full set of experimentally measured amino-acid preferences defining each ExpCM are shown in ?}. 
The ExpCM's use amino-acid preferences measured in deep mutational scanning of an H1 HA~\cite{doud2016accurate}, an H3 HA~\citep{lee2018deep}, or the average of the measurements for these two HAs.
The circle denotes the H1 clade and the triangle denotes the H3 clade. 
}
\end{figure}

@@

There are two deep mutational scanning datasets for HA that estimated amino-acid preferences for all sites.
One scan measured the site-specific amino-acid preferences of an H1 HA~\citep{doud2016accurate} and the other measured the preferences of an H3 HA~\citep{lee2018deep}.
These two HAs have only $\sim$42\% amino-acid identity, and so are separated by a large distance on the phylogenetic tree (see triangle and circle on \ref{fig:empirical_trees}).
The experimentally measured amino-acid preferences clearly differ between the the H1 and H3 HA at a substantial number of sites~\citep{lee2018deep}\jdbcomment{maybe also refer to your own supplementary figures}.
Therefore, we also created a third set of amino-acid preferences by averaging the preferences measured in the deep mutational scanning of the H1 and H3 HAs, under the conjecture that these averaged preferences might do a better job of describing the ``average'' constraint on sites across the full HA tree.
These three sets of HA amino-acid preferences define three different ExpCM's.
